Marlowe: implementing and analysing financial contracts on blockchain

### 2019-12-11 papers/marlowe2019/paper.tex
squish pictures in playground section a little to save space

For Marlowe to be usable in practice, users need to be able to design and develop Marlowe contracts, and also to understand how contracts will behave once deployed to the blockchain, but without before actually deploying them.

@@

\begin{figure}[]
    \includegraphics[width=1\textwidth]{input_composer.png}
\end{figure}

@@

\begin{figure}[]
    \includegraphics[width=0.8\textwidth]{tx_composer.png}
\end{figure}

@@

The final feature that we would like to present is the static analysis of contracts. As described in the previous section, it is possible to carry out a symbolic execution of a contract and then use a SMT solver to look for cases that could cause unwanted situations. The playground uses this to search for situations where contract execution would cause warnings. For example, suppose you write a contract that causes a payment of 450 Lovelace from Alice to Bob but the contract allows a situation where Alice has only deposited 350 Lovelace then the static analysis will find this and report it to the playground user.
\begin{figure}
    \includegraphics[width=1\textwidth]{static_analysis.png}
\end{figure}

>>>>

For Marlowe to be usable in practice, users need to be able to design and develop Marlowe contracts, and also to understand how contracts will behave once deployed to the blockchain, but without actually deploying them.

@@

\begin{wrapfigure}[6]{l}{0.5\textwidth}
    \vspace*{-0.1in}
    \includegraphics[scale=0.15]{input_composer.png}
\end{wrapfigure}

@@

\begin{wrapfigure}[6]{l}{0.5\textwidth}
    \vspace*{-0.2in}
    \includegraphics[scale=0.15]{tx_composer.png}
\end{wrapfigure}

@@

The final feature that we would like to present is the static analysis of contracts. As described in the previous section, it is possible to carry out a symbolic execution of a contract and then use a SMT solver to look for cases that could cause unwanted situations. The playground uses this to search for situations where contract execution would cause warnings. For example, suppose you write a contract that causes a payment of 450 Lovelace from Alice to Bob but the contract allows a situation where Alice has only deposited 350 Lovelace. The the static analysis will find this partial payment case and report it to the playground user with an example of how it could occur.
